Simulation Explorer

### 2018-06-03 inst/rmd/vis_sim.Rmd
Allow years and ages to have equal spatial distribution and revise cod simulation parameters

```{r setup, echo=FALSE}
library(plotly)
library(viridis)
knitr::opts_knit$set(root.dir = tmp$output_dir)
knitr::opts_chunk$set(echo = FALSE, fig.height = 7, fig.width = 8)
```

@@

```{r, eval = "sp_N" %in% names(sim)}
renderPlotly({
  plot_distribution(sim, ages = input$age, year = input$year, type = input$type,
                    scale = input$scale)
})
```

>>>>

```{r setup, echo=FALSE}
library(plotly)
library(viridis)
knitr::opts_chunk$set(echo = FALSE, fig.height = 7, fig.width = 8)
```

@@

```{r, eval = "sp_N" %in% names(sim)}
renderPlotly({
  plot_distribution(sim, ages = input$age, year = input$year, type = input$type,
                    scale = input$scale)
})

```
